Distributed Decision Making for Dynamic Formation of Web Services Communities

### 2015-06-01 papers/webservice-coalition-learning-omar-template/elsarticle-template-num.tex
changes
added notes

\begin{figure}%[!t]
\centerline{\includegraphics[width=1.75in]{figures/steps.eps}}
\caption{A summary of DDM decision profile generation steps}
\label{fig_steps}
\end{figure}

@@

Our goal is to create a decision making profile for each community in the $CFVS$ set. We are creating an environment where they can experience the outcomes of different strategies. The result will be a decision tree of the feasible and utility increasing moves over time.

>>>>

\begin{figure}%[!t]
\centerline{\includegraphics[width=6.0in]{figures/steps.eps}}
\caption{A summary of DDM decision profile generation steps}
\label{fig_steps}
\end{figure}

@@

Our goal is to create a decision making profile for each community in the $CFVS$ set. We are creating an environment where they can experience the outcomes of different strategies. The result will be a decision tree of the feasible and utility increasing moves over time. The root of decision tree represents a community in the $CFVS$ set, and the other nodes represents the result of the parent nodes' action of joining other communities and the expected utility of the community. Therefore, each node represents a community with a set of feature values of the parent node's community joining some other community, and an expected utility outcome of the newly formed community.
